---
title: "R Markdown Presentation & Plotly"
author: "Ridzuan Mohamad"
date: "6/17/2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Selected Variable and Description

No.| Variable | Description
---|----------|----------------------
1. |mpg      | Miles/(US) gallon
2. |cyl	     | Number of cylinders
3. |hp	     | Gross horsepower
5. |wt	     | Weight (1000 lbs)
6. |am	     | Transmission (0 = automatic, 1 = manual

## Datset Summary

```{r cars, echo = TRUE}
summary(mtcars[,c('mpg', 'cyl', 'hp', 'wt')])
```

## Boxplot

```{r, warning=FALSE, message=FALSE}
library(plotly)

mtcars$am[mtcars$am==0] <- 'Auto'
mtcars$am[mtcars$am==1] <- 'Manual'

plot_ly(mtcars, y = ~mpg, type = "box", color = ~factor(am))
```

## Scatter Plot

```{r, warning=FALSE, message=FALSE}
library(plotly)

mtcars$am[mtcars$am==0] <- 'Auto'
mtcars$am[mtcars$am==1] <- 'Manual'

plot_ly(
    mtcars, x = ~wt, y = ~mpg, type = "scatter", 
    color = ~factor(am), size = ~hp
)
```

